\documentclass[margin, 10pt]{res}
\usepackage{helvet} 
\setlength{\textwidth}{5.1in}
\begin{document}
\moveleft.5\hoffset\centerline{\large\bf Philipp Christian M\"unch, MSc, PhD (cand.)} 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'

\moveleft.5\hoffset\centerline{Personal Informations: Born in Coburg, Germany on Machr 14\textsuperscript{th}, 1988, German citizenship} % Your address
\moveleft.5\hoffset\centerline{Personal Adress: Leonrodstr. 27, 80636 Munich, Germany} % Your address
\moveleft.5\hoffset\centerline{Contact: (+49) 176-45871491, philipp.muench@helmholtz-hzi.de}

\begin{resume}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{ACADEMIC}
{\sl PhD (Cand.) (Medicine),}  \hfill 04/2015 - ongoing \\
University of Munich, Germany

{\sl Master of Science in Epidemiology,}  \hfill 10/2012 - 09/2014 \\
Major in Molecular and Clinical Epidemiology\\
University of Munich, Germany

{\sl Bachelor of Science / Engineer of Bioprocessinformatics,}  \hfill 10/2008 - 09/2012 \\
University of Applied Sciences Weihenstephan, Germany
 
%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{CAREER}

{\sl Graduate Research Associate} \hfill 04/2015 - ongoing \\
Computational Biology of Infection Research\\
Helmholtz Centre for Infection Research, Brunswick, Germany

{\sl Guest Researcher} \hfill 04/2015 - ongoing \\
AG Stecher, Bacteriology\\
Max-von-Pettenkofer Institute, University of Munich, Munich, Germany 

{\sl Graduate Research Associate} \hfill 04/2015 - 12/2015 \\
German Center for Infection Research (DZIF), \&\\
Computational Biology of Infection Research\\
Helmholtz Centre for Infection Research, Brunswick, Germany

{\sl Graduate Research Associate} \hfill 04/2015 - 12/2015 \\
Computational Biology of Infection Research\\
Helmholtz Centre for Infection Research, Brunswick, Germany

{\sl Graduate Research Associate (stipend)} \hfill 04/2014 - 12/2014 \\
Algorithmic Bioinformatics\\
Heinrich-Heine University Dusseldorf, Dusseldorf, Germany

{\sl Graduate Research Associate} \hfill 09/2012 - 03/2014 \\
Algorithmic Bioinformatics\\
Heinrich-Heine University Dusseldorf, Dusseldorf, Germany

{\sl Research Assistant} \hfill 01/2012 - 03/2012 \\
Computational Genomics and Epidemiology\\
Max Planck Institute for Informatics, Saarbr\"ucken, Germany

{\sl Research Assistant} \hfill 06/2011 - 12/2011 \\
Research Unit of Molecular Epidemiology\\
German Research Center for Environmental Health, Munich, Germany

{\sl Research Assistant} \hfill 08/2010 - 02/2011 \\
Computational Genomics and Epidemiology\\
Max Planck Institute for Informatics, Saarbr\"ucken, Germany\\

%----------------------------------------------------------------------------------------
%	Technology SKILLS SECTION
%----------------------------------------------------------------------------------------
%\newpage
\section{SKILLS} 

{\sl Programming Languages:} Python, Java, R, Matlab\\
{\sl Web Backend Technologies:} R-Studio Shiny, PHP, MySQL\\
{\sl Software Engineering:} Version control \\
{\sl Software:} Git, Vim, VirtualEnv, Docker\\
{\sl Laboratory:} Validated knowledge of annex 1 paragraph 3 TierSchVersV of Germany
 
%----------------------------------------------------------------------------------------
%	EXTRA-CURRICULAR ACTIVITIES SECTION
%----------------------------------------------------------------------------------------

\section{MEMBERSHIPS} 

German Society for Epidemiology (DGEpi), {\sl Member}\\
German Society for Infectiology (DGI), {\sl Member} 

%----------------------------------------------------------------------------------------
%	COMMUNITY SERVICE SECTION
%---------------------------------------------------------------------------------------- 

\section{COMMUNITY \\ SERVICE}

Hospital of Coburg, {\sl alternative service} \hfill 08/2007 - 04/2008 \\

%----------------------------------------------------------------------------------------
%	EXTRA-CURRICULAR ACTIVITIES SECTION
%----------------------------------------------------------------------------------------

\section{PUBLICATIONS}
%\vspace{1cm}
Bai, Y.*, M\"uller, D.B.*, Srinivas, G.*, Garrido-Oter, R.*, Potthoff, E., Rott, M., Dombrowski, N., \underline{M\"unch, P.C.}, Spaepen, S., Remus-Emsermann, M. and H\"uttel, B., 2015. Functional overlap of the Arabidopsis leaf and root microbiota. \textbf{Nature}.\hfill IF:  38.1\footnote[1]{impact factors updated on Sep. 2016}

Bulgarelli, D., Garrido-Oter, R., \underline{M\"unch, P.C.}, Weiman, A., Dr\"oge, J., Pan, Y., McHardy, A.C. and Schulze-Lefert, P., 2015. Structure and function of the bacterial root microbiota in wild and domesticated barley. \textbf{Cell host \& microbe}, 17(3), pp.392-403.\hfill IF: 12.3

Hacquard, S.*, Kracher, B.*, Hiruma, K., \underline{M\"unch, P.C.}, Garrido-Oter, R., Thon, M.R., Weimann, A., Damm, U., Dallery, J.F., Hainaut, M. and Henrissat, B., 2016. Survival trade-offs in plant roots during colonization by closely related beneficial and pathogenic fungi. \textbf{Nature communications}, 7.\hfill IF: 11.3

Brugiroux, S., Beutler, M., Carina, P., Garzetti, D, Ruscheweyh, H., Ring, D., Diehl, M., Herp, S., Loetscher, Y., Hussain, S., Bunk, B., Pukall, R., Huson, D., \underline{M\"unch, P.C.}, McHardy, A.C., McCoy, K. , Macpherson, A., Loy A., Clavel, T., Berry, T. Genome-guided design of a novel defined mouse microbiota that confers colonization resistance against Salmonella enterica serovar Typhimurium. \textbf{Nature microbiology} \hfill IF: NA

Kloetgen, A., \underline{M\"unch, P.C.}, Borkhardt, A., Hoell, J.I. and McHardy, A.C., 2014. Biochemical and bioinformatic methods for elucidating the role of RNA–protein interactions in posttranscriptional regulation. \textbf{Briefings in functional genomics}, \hfill IF: 3.1

Krause, S., Bremges, A., \underline{M\"unch, P.C.}, McHardy, A.C., Laboratory cultivation of acidophilic nanoorganisms. Physiological and bioinformatic dissection of a stable laboratory co-culture. \textbf{bioRxiv} \hfill IF: NA

Duggimpudi, S., Maney S.K., Kloetgen, A., \underline{M\"unch, P.C.}, Hezaveh, K., Shaikalishahi, H., Hoyer W., McHardy, A.C., Lang, P.A., Borkhardt, A., Hoell, J.I., 2017. Musashi 2 regulates Interleukin-6 signaling through its RNA-binding activity. \textit{(submitted)}

\underline{M\"unch, P.C.}, Stecher, B., McHardy, A.C., EDEN: evolutionary dynamics within environments \textit{(under revision)}

\underline{M\"unch, P.C.}*, Goeser, F.*, Krämer, B., McHardy, A.C., Lutz, P., Kaczmarek, D.,  Finnemann, C., Nischalke, H., Geffers, R., Parcina, M.,  Strassburg,  C.P., Hörauf, A., McHardy, A.C.,  Nattermann, J., Bekeredjian-Ding, I., Spengler, U., Specific alterations of the intestinal microbiome in autoimmune hepatitis show partially liver disease-specific patterns being also related to the extent of liver parenchymatous tissue remodeling \textit{(in prepreation)} \hfill IF: NA

* joint first-authorship
%----------------------------------------------------------------------------------------

\end{resume}
\end{document}